Efficiently stable presentations from error-correcting codes

### 2023-10-10 efficient_stability.tex
Updates from Overleaf

\author[1]{Michael Chapman}
\author[2]{Thomas Vidick}
\author[3]{Henry Yuen}
\affil[1]{}
\affil[2]{ Faculty of Mathematics and Computer Science, Weizmann Institute of Science, Israel}
\affil[3]{Department of Computer Science, Columbia University, USA}

@@

\begin{abstract}
We introduce a notion of \emph{efficient stability} for finite presentations of groups. Informally, a finite presentation using generators $S$ and relations $R$ is \emph{stable} if any map from $S$ to unitaries (say, in some finite von Neumann algebra) that approximately satisfies the relations (in the tracial norm) is close to the restriction of a representation of $G$ to the subset $S$. This notion and variants thereof have been extensively studied in recent years, in part motivated by connections to property testing in computer science. The novelty in our work is the focus on \emph{efficiency} which, informally, places an onus on small presentations (of size, say, logarithmic in the group size) and aims to achieve non-trivial tradeoffs between it and the stability---as, intuitively, more generators and relations place more constraints on the approximate homomorphism, making stability easier to achieve---whereas we wish to minimize the number of variables and constraints.

Equipped with the new definition we give examples. We first show a general method for constructing candidate stable presentations of $\Z_2^k$ from linear error-correcting codes that have an additional property known as \emph{local testability}. While we cannot show that the method always leads to stable presentations, we leverage recent results in the study of nonlocal games in quantum information theory (Ji et al., Discrete Analysis 2021) to show that a specific instantiation of our construction, based on the Reed-Muller family of codes, leads to a stable presentation of $\Z_2^k$ of size $\poly\log(k)$ only. As an application we combine this result with recent work of de la Salle (arXiv:2204.07084) to re-derive a key building block in the recent disproof of Connes' Embedding Problem via complexity theory (Ji et al., arXiv:2001.04383), the quantum low-degree test of Natarajan and Vidick (IEEE FOCS'18). 
\end{abstract}

@@

A finer property which concerns us here is the \emph{soundness} of the code, a parameter that is connected to the notion of \emph{local testability}. A code can be (non-uniquely) specified through a \emph{parity-check matrix} $h\in\F^{m\times n}$ as $\code = \ker h$. The rows of $h$ are thought of as constraints (``parity checks'') that specify $\code$ as a subspace of $\F^n$. A code is called locally testable \emph{with soundness $\rho$} if for every $x\in \F^n$, $\frac{1}{m}|hx|\geq \rho \, \frac{1}{n}\, d(x,\code)$, where $d(x,\code)$ denotes the minimum of $|x-c|$ over $c\in \code$.  Ideally one would like to design families of good codes such that in addition $\rho$ is bounded below by a constant independent of $n$.\footnote{Note that in principle a code can have a small minimal distance $d$, and still be locally testable with soundness $\rho>0$. So a family of codes can be ``locally testable'' without being ``good.''} This is a challenging task, and the construction of families of good locally testable codes was only achieved very recently~\cite{LTC_DELLM}.

The terminology ``locally testable'' comes from an interpretation of $\frac{1}{m}|hx|$ as the probability of rejection of a natural ``tester'' for $\code$, i.e.\ an algorithm that on input $x$ checks a randomly chosen row $h_i$ of $h$ and accepts if and only if $h_i\cdot x = \sum_j h_{ij} x_j =0$.  Thus a code is called locally testable if words that are far from the code have a high probability of being rejected according to this tester. This notion plays a central role in applications of codes to complexity theory~\cite{babai1991non,PCP_thm}, and continues to be actively studied, see e.g.~\cite{LTC_DELLM,LTC_Panteleev_Kalachev} for a recent breakthrough on the topic.

@@

We observe that $1$-dimensional representations, i.e.\ maps from $S=\{x_1,\ldots,x_n\}$ to $\{-1,1\}$ that satisfy all relations $R$, are in one-to-one correspondence with elements of $\code$. Moreover, \emph{approximate} $1$-dimensional representations, i.e.\ maps from  $S=\{x_1,\ldots,x_n\}$ to $\{-1,1\}$ that satisfy a fraction $1-\eps$ of all relations for small $\eps$, can be identified with words $x\in\F_2^n$ such that $\frac{1}{m}|hx|\leq C\eps$ for some constant $C$ depending on the ratio $m/n$.\footnote{In principle we could allow the map to range over $U(\C)$ instead of $\{-1,1\}$. In general we will allow this; but for the purposes of this introduction it is simpler to restrict to the $\{-1,1\}$-valued case (which corresponds to considering the relations $x_j^2=e$ as ``hard'' constraints that always need to be satisfied).} In particular, and somewhat loosely speaking, we notice that $\code$ is locally testable with soundness $\rho$ if and only if approximate $1$-dimensional representations of $G(h)$ are always close to $1$-dimensional representations.

@@

This example and many others show that the notion of stability is, in general, highly sensitive to the notion of closeness considered. Returning to our main concern, so far we have argued that 
stability of approximate \emph{$1$-dimensional} representations of the presentation $G(h)$ is connected to local testability of the code $\ker h$. In the case of $1$-dimensional representations of course the choice of norm does not matter; however, the choice of measuring the error on average over relations, as opposed to e.g.\ taking the maximum, is one in which we depart from most of the literature. We will motivate this choice further below; but before we can continue we must pause to introduce the key definitions that our work builds on. For the purposes of the introduction we focus the discussion on finite-dimensional representations; in the main paper we handle the general case of representations in a tracial von Neumann algebra. Let $\mU(\C^d)$ denote the unitary operators on $\C^d$, and for a set $S$ let $\mF(S)$ denote the free group generated by the elements of $S$. For $X\in \C^{d\times d}$ let $\|X\|_f^2 = \frac{1}{d}\Tr(X^* X)$ denote the normalized Hilbert-Schmidt norm.

\begin{definition}[Almost homomorphism]\label{def:approx-hom-intro}
Let $G = \langle S:R\rangle $ be a finitely presented group and $\mu_R$ a distribution on $R$. An $(\eps,\mu_R)$-almost homomorphism of $G$ is a homomorphism $\phi:\mF(S)\to\mU(\C^d)$ for some $d\geq 1$ such that
\[ \Es{r\sim \mu_R} \big\|  \phi(r) - \Id \big \|_f^2 \,\leq\, \eps\;.\]
\end{definition}

As already mentioned this definition makes two importance choices: firstly, to measure closeness in the Hilbert-Schmidt norm, and secondly, to measure it on average over the choice of a relation. Next we give our definition for a finitely presented group to be stable; see Definition~\ref{def:eff-stab} for the general setting.

\begin{definition}[Stability]\label{def:eff-stab-intro}
Let $G = \langle S:R\rangle $ be a finitely presented group, $\mu_S$ a distribution on $S$ and $\mu_R$ a distribution on $R$. For $\delta:[0,1]\to[0,1]$ such that $\lim_{t\to 0}\delta(t)=0$ and an integer $d\geq 1$ we say that the presentation $G=\langle S:R\rangle$ is $(\delta,\mu_S,\mu_R,d)$-stable if for every $(\eps,\mu_R)$-almost homomorphism $\phi: \mF(S) \to \mU(\C^d)$ there is a unitary representation $\psi: G \to \mU(\C^d)$ such that
\[ \Es{s\sim \mu_S} \big\|  \phi(s) - \psi(s) \big \|_f^2 \,\leq\, \delta(\eps)\;.\]
We refer to any function $\delta$ satisfying the above as a ``modulus of stability'' of the presentation.
\end{definition}

@@

\paragraph{Related works on stability.} The general question of group stability was first formulated by Ulam~\cite{ulam1960collection}, and later studied by Kazhdan for the case of the operator norm~\cite{kazhdan1982e}.

@@

\tnote{more? open questions?}

@@

\paragraph{Acknowledgments.} TV is supported by a research grant from the Center for New Scientists at the Weizmann Institute of Science, a Simons Investigator award, AFOSR Grant No. FA9550-22-1-0391, and ERC Consolidator Grant VerNisQDevS (101086733). HY is supported by AFOSR award FA9550-21-1-0040, NSF CAREER award CCF-2144219, and the Sloan Foundation.

@@

We consider the following presentation for the Pauli group:
\begin{align*}
 \pauli_k \,=\, \big\langle \{J\}\cup  \{(a,b): a,b\in \Z_2^k\} &: (a,0)^2=(0,b)^2=J^2=e,\; [a,J]=[b,J]=e,\\
&\qquad  (a,0)(b,0) = J^{a\cdot b} (a,b) \; \quad \forall a,b\big\rangle\;.
\end{align*}
This presentation is not quite the multiplication table presentation (it has $2^{2k}+1$ generators, whereas $|\pauli_k|=2^{2k+1}$), but it is not far from it.  
Applying Theorem~\ref{thm:gh} we obtain the following consequence.%, which we again state only for the case of a subclass of approximate homomorphisms and the class of finite-dimensional matrix algebras\tnote{again, not sure what we want ultimately}.

\begin{corollary}[Pauli braiding test]
Let $\phi_X,\phi_Z:\Z_2^k \to \mU(\mM)$ be such that for all $W\in \{X,Z\}$,
\[ \Es{a,b\in \Z_2^k} \big\| \phi_W(a)\phi_W(b)-\phi_W(a+b) \big\|_\tau^2 \,\leq\,\eps\;,\]
and
\[ \Es{a,b\in \Z_2^k} \big\| \phi_X(a)\phi_Z(b)- (-1)^{a\cdot b} \phi_Z(b)\phi_X(a) \big\|_{\tau}^2 \,\leq\,\eps\;.\]
Then there is a projection $P\in \mM_\infty$ such that if $\mN=P\mM_\infty P$ then $\mN\simeq (M_2(\C))^{\otimes k} \otimes \mN'$ for some $\mN'$, and a
partial isometry $w\in P\mM_\infty I_\mM$ such that for all $W\in \{X,Z\}$, 
\[ \Es{W\in \Z_2^k} \big\| \phi_W(a) - w^* \big(\sigma_W(a)\otimes \Id_{\mN'}\big) w \big\|_{\tau}^2 \,=\, O(\eps)\;.\]
\end{corollary}

@@

\begin{proof}[Proof sketch]
Define $\phi:\pauli_k \to \mU(\mM)$ by $\phi(J^c (a,b))= (-1)^c \phi_X(a)\phi_Z(b)$, where $c\in \{\pm 1\}$ and $a,b\in \Z_2^k$. Then it is not hard to verify that the assumptions of the corollary imply that  $\phi$ is an $O(\eps)$-almost homomorphism for the multiplication table presentation of $\pauli_k$. Applying Theorem~\ref{thm:gh} we find a unitary representation $\phi'$ of $\pauli_k$ on some $(\mN,\tau^\mN)$ that is $O(\eps)$-close to $\phi$. To conclude we observe that the only irreducible unitary representation of $\pauli_k$ that sends $J$ to $-1$ is the representation by the Pauli matrices; furthermore, all other irreducible representations are $1$-dimensional. From there it is not hard to show that, if we restrict $\phi'$ to its support on the Pauli matrix representation, the result remains $O(\eps)$-close to $\phi$. We omit the details. 
\end{proof}

@@

\begin{lemma}\label{lem:eff-pauli}
  Let $\mC$ be the class of tracial von Neumann algebra. Let $\mu_R$ be the equal mixture of the uniform distribution on all words $ [x_i,x_j]$, $[z_i,z_j]$, $[x_i,z_j]$ ($i\neq j$), the uniform distibution over all $[x_i,z_i]$, $[x_i,J]$, $[z_i,J]$, $x_i^2$ and $z_i^2$, and $J^2$. Let $\mu_S$ be the marginal of $\mu_R$, as described in Remark~\ref{rk-mus}. Then 
 the presentation~\eqref{eq:z2-efficient} is $(O(k\eps),\mu_S,\mu_R,\mC)$-stable.
\end{lemma}

\begin{proof}
This follows from Lemma~\ref{lem:eff-z2} and Theorem~\ref{thm:dls-gap}.
\end{proof}

>>>>

\author[1]{Michael Chapman}
\author[2]{Thomas Vidick}
\author[3]{Henry Yuen}
\affil[1]{Courant Institute of Mathematical Sciences, 
	New York University, USA}
\affil[2]{ Faculty of Mathematics and Computer Science, Weizmann Institute of Science, Israel}
\affil[3]{Department of Computer Science, Columbia University, USA}

@@

\begin{abstract}
\mnote{After reading the abstract a few more times, I agree with Henry. I commented out the things that seemed to me superfluous. Regarding the last remark of "more gen and relations means more stability", I have counter examples of that. So I prefer to not state it, even heuristically, that way}We introduce a notion of \emph{efficient stability} for finite presentations of groups. Informally, a finite presentation using generators $S$ and relations $R$ is \emph{stable} if any map from $S$ to unitaries 
%(say, in some finite von Neumann algebra) 
that approximately satisfies the relations (in the tracial norm) is close to the restriction of a representation of $G$ to the subset $S$. This notion and variants thereof have been extensively studied in recent years, in part motivated by connections to property testing in computer science. The novelty in our work is the focus on \emph{efficiency}, which, informally, places an onus on small presentations --- in the sense of encoding length.  
%(of size, say, logarithmic in the group size)
The goal in this setup is to achieve non-trivial tradeoffs between the presentation length and its modulus of stability.
%---as, intuitively, more generators and relations place more constraints on the approximate homomorphism, making stability easier to achieve---whereas we wish to minimize the number of variables and constraints.

\mnote{Here I genuinely changed the phrasing. I don't think it is currently very good, but it is better than it was. Feel free to iterate:} Equipped with this tradeoff in mind, we analyze various natural examples of presentations. We provide a general method for constructing presentations of $\Z_2^k$ from linear error-correcting codes. We observe that the resulting presentation has a weak form of stability exactly when the code is  \emph{locally testable}.\mnote{I have a problem with the notion of locally testable. The notion reffers ususally to testable LDPCs. We do not need the low density to define our notions and construction, only the testable part. I think we should change it to just testable codes... What do you think? This appears throughout the intro... It won't be a major change} This raises the question of whether locally testable codes give rise to genuinely stable presentations using this method.  While we cannot show that in general, we leverage recent results in the study of non-local games in quantum information theory (Ji et al., Discrete Analysis 2021) to show that a specific instantiation of our construction, based on the Reed-Muller family of codes, leads to a stable presentation of $\Z_2^k$ of size $\poly\log(k)$ only. As an application, we combine this result with recent work of de la Salle (arXiv:2204.07084) to re-derive  the quantum low-degree test of Natarajan and Vidick (IEEE FOCS'18), which is a key building block in the recent refutation of Connes' Embedding Problem via complexity theory (Ji et al., arXiv:2001.04383). 
\end{abstract}

@@

A finer property which concerns us here is the \emph{soundness} of the code, a parameter that is connected to the notion of \emph{local testability}. A code can be (non-uniquely) specified through a \emph{parity-check matrix} $h\in\F^{m\times n}$ as $\code = \ker h$. The rows of $h$ are thought of as constraints (``parity checks'') that specify $\code$ as a subspace of $\F^n$. A code is called locally testable \emph{with soundness $\rho$} if for every $x\in \F^n$, $\frac{1}{m}|hx|\geq \rho \, \frac{1}{n}\, d(x,\code)$, where $d(x,\code)$ denotes the minimum of $|x-c|$ over $c\in \code$.  Ideally one would like to design families of good codes such that in addition $\rho$ is bounded below by a constant independent of $n$.\footnote{Note that in principle a code can have a small minimal distance $d$, and still be locally testable with soundness $\rho>0$. So a family of codes can be ``locally testable'' without being ``good.''} This is a challenging task, and the construction of families of good locally testable codes was only achieved very recently~\cite{LTC_DELLM,LTC_Panteleev_Kalachev}.

The terminology ``locally testable'' comes from an interpretation of $\frac{1}{m}|hx|$ as the probability of rejection of a natural ``tester'' for $\code$, i.e.\ an algorithm that on input $x$ checks a randomly chosen row $h_i$ of $h$ and accepts if and only if $h_i\cdot x = \sum_j h_{ij} x_j =0$.  Thus a code is called locally testable if words that are far from the code have a high probability of being rejected according to this tester. This notion plays a central role in applications of codes to complexity theory~\cite{babai1991non,PCP_thm}, and continues to be actively studied. See e.g.~\cite{LTC_DELLM,LTC_Panteleev_Kalachev} for a recent breakthrough on the topic.

@@

We observe that $1$-dimensional representations, i.e.\ maps from $S=\{x_1,\ldots,x_n\}$ to $\{-1,1\}$ that satisfy all relations $R$, are in one-to-one correspondence with elements of $\code$. Moreover, \emph{approximate} $1$-dimensional representations, i.e.\ maps from  $S=\{x_1,\ldots,x_n\}$ to $\{-1,1\}$ that satisfy a fraction $1-\eps$ of all relations for small $\eps$, can be identified with words $x\in\F_2^n$ such that $\frac{1}{m}|hx|\leq C\eps$ for some constant $C$ depending on the ratio $m/n$.\footnote{In principle we could allow the map to range over $U(\C)$ instead of $\{-1,1\}$. In general we will allow this; but for the purposes of this introduction it is simpler to restrict to the $\{-1,1\}$-valued case (which corresponds to considering the relations $x_j^2=e$ as ``hard'' constraints that always need to be satisfied).} In particular, we notice that $\code$ is locally testable with soundness $\rho$ if and only if $\eps$-approximate $1$-dimensional representations of $G(h)$ are $\nicefrac{\eps}{\rho}$-close to genuine $1$-dimensional representations.

@@

This example and many others show that the notion of stability is, in general, highly sensitive to the notion of closeness considered. Returning to our main concern, so far we have argued that 
stability of approximate \emph{$1$-dimensional} representations of the presentation $G(h)$ is connected to local testability of the code $\ker h$. In the case of $1$-dimensional representations of course the choice of norm does not matter; however, the choice of measuring the error on average over relations, as opposed to e.g.\ taking the maximum, is one in which we depart from most of the literature. We will motivate this choice further below; but before we can continue we must pause to introduce the key definitions that our work builds on. For the purposes of the introduction we focus the discussion on finite-dimensional representations; in the main paper we handle the general case of representations in a tracial von Neumann algebra. Let $\mU(\C^d)$ denote the unitary operators on $\C^d$, and for a set $S$ let $\mF(S)$ denote the free group generated by the elements of $S$. For $X\in \C^{d\times d}$ let $\|X\|_{hs}^2 = \frac{1}{d}\Tr(X^* X)$ denote the (normalized) Hilbert-Schmidt norm.\footnote{This norm is also commonly called the normalized \emph{Frobenius} norm. Following \cite{dechiffre_glebsky_lubotzky_thom_2020}, it became common in stability theory to call the normalized version Hilbert--Schmidt and the un-normalized version Frobenius. In any case, in the main part of this paper, we relate to it as the tracial norm because of the von Neumann algebraic framework we use.}

\begin{definition}[Almost homomorphism]\label{def:approx-hom-intro}
Let $G = \langle S:R\rangle $ be a finitely presented group and $\mu_R$ a distribution on $R$. An $(\eps,\mu_R)$-almost homomorphism of $G$ is a homomorphism $\phi:\mF(S)\to\mU(\C^d)$ for some $d\geq 1$ such that
\[ \Es{r\sim \mu_R} \big\|  \phi(r) - \Id \big \|_{hs}^2 \,\leq\, \eps\;.\]
\end{definition}

As already mentioned this definition makes two important choices: firstly, to measure closeness in the Hilbert-Schmidt norm, and secondly, to measure it on average over the choice of a relation. Next we give our definition for a finitely presented group to be stable; see Definition~\ref{def:eff-stab} for the general setting.

\begin{definition}[Stability]\label{def:eff-stab-intro}
Let $G = \langle S:R\rangle $ be a finitely presented group, $\mu_S$ a distribution on $S$ and $\mu_R$ a distribution on $R$. For $\delta:[0,1]\to[0,1]$ such that $\lim_{t\to 0}\delta(t)=0$ and an integer $d\geq 1$ we say that the presentation $G=\langle S:R\rangle$ is $(\delta,\mu_S,\mu_R,d)$-stable if for every $(\eps,\mu_R)$-almost homomorphism $\phi: \mF(S) \to \mU(\C^d)$ there is a unitary representation $\psi: G \to \mU(\C^d)$ such that
\[ \Es{s\sim \mu_S} \big\|  \phi(s) - \psi(s) \big \|_{hs}^2 \,\leq\, \delta(\eps)\;.\]
We refer to any function $\delta$ satisfying the above as a ``modulus of stability'' of the presentation.
\end{definition}

\begin{remark}[The $L^\infty$ analogue]\label{rem:L^infty_analogue_defn}
    As mentioned  before, it is common to call a homomorphism $\phi\colon \mF(S)\to \mU(\complex^d)$ an $\eps$-almost homomorphism of $G=\langle S\colon R\rangle,$  if $\max_{r\in R}\Vert \phi(r)-\Id\Vert_{hs}^2\leq \eps$. Furthermore, the distance between two homomorphisms $\phi,\psi\colon \mF(S)\to \mU(\complex^d)$ is ususally taken to be $\max_{s\in S}\Vert \phi(s)-\psi(s)\Vert_{hs}^2$. The notion of stability induced by these definitions of `almost' and `close' is more commonly used. Note that when studying a fixed finitely presented group, and without caring about the exact modulus of stability, there is no difference between the two definitions.  But, when one cares about the modulus of stability, which is the case  when viewing stability as a property testing problem, our framework is the more natural one. 
\end{remark}

@@

\paragraph{Related works on stability.} The general question of group stability was first formulated by Ulam~\cite{ulam1960collection}, and later studied by Kazhdan for the case of the operator norm~\cite{kazhdan1982e}. See the introduction of \cite{ioana2020stability} for a thorough history of these problems through the lens of approximate commutation (cf.  \cite{von1942approximative,voiculescu1983asymptotically}). A major contribution was done by \cite{hadwin2018stability}, in which they characterized the stable amenable groups according to properties of their space of characters.

@@

\tnote{more? open questions?}\mnote{If we have open problems, maybe we should collect them at the end? Not sure about that. Did you think of any open problems other than the permutation analogue of the quantum soundness of the low-deg test?}

@@

\paragraph{Acknowledgments.} 
MC acknowledges with gratitude the Simons Society of Fellows and is supported by a grant from the Simons Foundation (N. 965535).

TV is supported by a research grant from the Center for New Scientists at the Weizmann Institute of Science, a Simons Investigator award, AFOSR Grant No. FA9550-22-1-0391, and ERC Consolidator Grant VerNisQDevS (101086733). HY is supported by AFOSR award FA9550-21-1-0040, NSF CAREER award CCF-2144219, and the Sloan Foundation.

@@

We consider the following presentation for the Pauli group \mnote{This is not the correct presentation. We use only $(a,0)$ and $(0,b)$ as generators (and not all pairs as currently written). Also, the anti commutation relation is in the other direction isn't it? I don't want to mess something because I am not sure which presentation you were aiming for, but this has typos in it for sure. Lastly, the commutation with $J$ should be of pairs $(a,0)$ and $(0,b)$ and not just $a$ and $b$}:
\begin{align*}
 \pauli_k \,=\, \big\langle \{J\}\cup  \{(a,b): a,b\in \Z_2^k\} &: (a,0)^2=(0,b)^2=J^2=e,\; [a,J]=[b,J]=e,\\
&\qquad  (a,0)(b,0) = J^{a\cdot b} (a,b) \; \quad \forall a,b\big\rangle\;.
\end{align*}
This presentation is not quite the multiplication table presentation (it has $2^{2k}+1$ generators, whereas $|\pauli_k|=2^{2k+1}$), but it is not far from it.  \mnote{The number of generators should be $2^{k+1}+1$ and not $2^{2k}+1$.}
Applying Theorem~\ref{thm:gh} we obtain the following consequence.%, which we again state only for the case of a subclass of approximate homomorphisms and the class of finite-dimensional matrix algebras\tnote{again, not sure what we want ultimately}.

\begin{corollary}[Pauli braiding test]\label{cor:Pauli-brading_is_stable}
Let $\phi_X,\phi_Z:\Z_2^k \to \mU(\mM)$ be such that for all $W\in \{X,Z\}$,
\[ \Es{a,b\in \Z_2^k} \big\| \phi_W(a)\phi_W(b)-\phi_W(a+b) \big\|_\tau^2 \,\leq\,\eps\;,\]
and
\[ \Es{a,b\in \Z_2^k} \big\| \phi_X(a)\phi_Z(b)- (-1)^{a\cdot b} \phi_Z(b)\phi_X(a) \big\|_{\tau}^2 \,\leq\,\eps\;.\]
Then there is a projection $P\in \mM_\infty$ such that if $\mN=P\mM_\infty P$ then $\mN\simeq (M_2(\C))^{\otimes k} \otimes \mN'$ for some $\mN'$, and a
partial isometry $w\in P\mM_\infty I_\mM$ such that for all $W\in \{X,Z\}$, 
\[ \Es{W\in \Z_2^k} \big\| \phi_W(a) - w^* \big(\sigma_W(a)\otimes \Id_{\mN'}\big) w \big\|_{\tau}^2 \,=\, O(\eps)\;.\]
\end{corollary}

@@

\begin{proof}[Proof sketch]
\mnote{This proof sketch is very confusing. We think of the elements of $P_k$ as $\pm \sigma_X(a)\sigma_Z(b)$, not as $J^{\pm 1}(a,b)$. This is a parametrization of the generators in the specific presentation we provided, and which does not play a role here in the proof. Actually, this is part of what is confusing. The corollary is essentially that almost homomorphisms w.r.t the above presentation of $P_k$ can be translated to almost homs of $P_k$ w.r.t the multiplication table pres without changing the $\eps$ too much. We developed the proper language to make Corollary \ref{cor:Pauli-brading_is_stable} much shorter. We should have just stated that the presentation we gave for $P_k$ is stable, and furthermore, that when $J$ is mapped to $-1$, then the close by representation must be of the form $\Id\otimes P_k$. Anyway, maybe we can discuss this a bit and then I'll do the changes. Didn't want to mess up if this is the way you wanted everything to look like.  }
Define $\phi:\pauli_k \to \mU(\mM)$ by $\phi(J^c (a,b))= (-1)^c \phi_X(a)\phi_Z(b)$, where $c\in \{\pm 1\}$ and $a,b\in \Z_2^k$. Then it is not hard to verify that the assumptions of the corollary imply that  $\phi$ is an $O(\eps)$-almost homomorphism for the multiplication table presentation of $\pauli_k$. Applying Theorem~\ref{thm:gh} we find a unitary representation $\phi'$ of $\pauli_k$ on some $(\mN,\tau^\mN)$ that is $O(\eps)$-close to $\phi$. To conclude we observe that the only irreducible unitary representation of $\pauli_k$ that sends $J$ to $-1$ is the representation by the Pauli matrices; furthermore, all other irreducible representations are $1$-dimensional. From there it is not hard to show that, if we restrict $\phi'$ to its support on the Pauli matrix representation, the result remains $O(\eps)$-close to $\phi$. We omit the details. 
\end{proof}

@@

\begin{lemma}\label{lem:eff-pauli}
  Let $\mC$ be the class of tracial von Neumann algebras. Let $\mu_R$ be the following sampling procedure: With equal probability do one of the following
  \begin{itemize}
      \item Choose $J^2=e$.
      \item Sample $i\in [k]$ uniformly and choose $x_i^2=e$ (respectively, $z_i^2=e$).
      \item Sample $i\in [k]$ uniformly and choose $[x_i,z_i]=J$.
      \item Sample $i\neq j\in [k]$ uniformly at random and choose $[x_i,x_j]=e$ (respectively, $[z_i,z_j]=e$ or $[x_i,z_j]=e$).
  \end{itemize}
  Let $\mu_S$ be the marginal of $\mu_R$, as described in Remark~\ref{rk-mus}. Then 
 the presentation~\eqref{eq:pauli-efficient} is $(O(k\eps),\mu_S,\mu_R,\mC)$-stable.
\end{lemma}

\begin{proof}
This follows from Lemma~\ref{lem:eff-z2} and Theorem~\ref{thm:dls-gap}, in a similar manner to our proof sketch of Corollary \ref{cor:Pauli-brading_is_stable}.
\end{proof}
